\vfill World of Warcraft's New Way to Get You Hooked

### 2013-02-13 paper.tex
Somehow managed to get the abstract below 75 words...

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
In July of 2011, Blizzard Entertainment replaced its World of Warcraft trial model with a new ``World of Warcraft Starter Edition'', allowing players to try the game for free indefinitely with certain restrictions. \cite{starterEditionNewsRelease} Some studies have shown a positive correlation between time spent playing Massively Multiplayer Online Role-Playing Games (MMORPGs) and addiction to MMORPGs. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} Is it ethical for Blizzard to have switched to this new model?

Companies have been providing demo versions of software for as long as software has been available. I see no difference between World of Warcraft's new business model and other software demos that I've used. Based on the principles of Utilitarianism \cite{Utilitarianism}, restricting a free demo on the basis of a few scattered cases of mental instability is unethical, therefore World of Warcraft's new model \emph{is} ethical.
\end{abstract}

@@

% Undisputed facts in your domain of concern that lead to the question. Do not judge these facts or make anything like an argument for a conclusion. Just note the undisputed facts that give a general motivation for the question. Conclude this section with facts that lead to a controversy. The reader should naturally be asking the question you'll be asking by that point in your paper. In general, attach your facts to a specific case – the more specific and detailed the facts, the better for your analysis. Do NOT tell the whole story, ONLY the facts required to "raise" your question. Do not give a bulleted list of facts, write a simple narrative about the state of the world" in your given problem domain. Cite all facts to their sources.

>>>>

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
World of Warcraft has a ``Starter Edition'' allowing players access for free indefinitely with restrictions. \cite{starterEditionNewsRelease} Studies show a correlation between time playing and addiction to Massively Multiplayer Online Role-Playing Games (MMORPGs) like World of Warcraft. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} Is it ethical for World of Warcraft to use this model?

Based on the principles of Utilitarianism \cite{Utilitarianism}, restricting a free demo on the basis of a few scattered cases of mental instability is unethical, therefore World of Warcraft's ``Starter Edition'' \emph{is} ethical.
\end{abstract}

@@
